---
title: "KerusCloud VPV"
author: "Gareth Burns"
format: html
editor: visual
execute: 
  echo: false
  warning: false
---

```{r}
library(tidyverse, warn.conflicts = FALSE)


# Local Data --------------------------------------------------------------

LikertData <-
  readxl::read_excel(path = "KerusCloud Virtual Population Visualisations.xlsx", sheet = "Sheet1")


# Data Wrangling ----------------------------------------------------------
scale <-  c(
  "Not Important" = 1,
  "Slightly Important" = 2,
  "Moderately Important" = 3,
  "Very Important" = 4,
  "Extremely Important" = 5
)

colnames(LikertData)[6:15] <-
  gsub('.*\\.', '', colnames(LikertData[6:15]))

# LikertData[,6:15] <- lapply(LikertData[,6:15], factor, levels = scale)
# dataSummary <- likert(LikertData[,6:15])
response <- nrow(LikertData)

data <-  LikertData |>
  gather("Feature",
         "Response",
         -Id,
         -`Start time`,
         -`Completion time`,
         -`Email`,
         -Name) |>
  mutate(Response = factor(
    Response,
    levels = c(
      "Not Important",
      "Slightly Important",
      "Moderately Important",
      "Very Important",
      "Extremely Important"
    )
  )) |> 
  group_by(Feature, Response) |>
  summarise(count = n(), 
            Percent = n()/response *100)


```


## KerusCloud VPV

Users were provide 10 features and asked the question **"How important is the feature?"** and allowed the following responses on the **Likert Scale (1-5)**

-    Not Important

-    Slightly Important

-    Moderately Important

-    Very Important

-    Extremely Important

A total of **`r nrow(LikertData)`** responses were gathered.

## Priority List

@fig-lollipot displays the mean response from all respondents on each feature. 

```{r}
#| label: fig-lollipot
#| fig-cap: "Lollipop chart"
#| echo: false
data1 <- data
data1$Response <- scale[match(data1$Response, names(scale))]

data1 <- data1 |>
  group_by(Feature) |>
  summarise(Mean = mean(Response)) |>
  arrange(Mean)

ggplot(data1, aes(x = Mean, xend = 1, y = reorder(Feature, Mean), yend = Feature)) +
  geom_segment() +
  geom_point(size = 8, colour = "lightblue") +
  geom_text(aes(label = Mean)) +
  ggtitle(label = "Virtual Population Visualisation", 
          subtitle = "Average Response of Feature on Likert scale (1-5)") +
  scale_x_continuous(limits = c(1, 5))+
  xlab("Mean Response") +
  ylab("Feature") +
  theme_classic() 


```



## In agreement?

@fig-stackedbar displayed if there's a broad agreement in the responses. 

```{r}
#| label: fig-stackedbar
#| fig-cap: "Stacked Bar Chart"
#| echo: false
ggplot(data = data, aes(x = Percent, fill = Response, y = Feature)) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "YlGn")+
  labs(
    title = "KerusCloud VPV",
    subtitle = "Reponse to 'How important would you view the feature?'",
    x = "Response (%)",
    y = "Feature"
  ) +
  theme_classic() +
  theme(legend.position = "bottom")
```
